### 2020-05-06 thesis/chapter-1.tex
working on introduction fitting together.

Due to their low volumetric energy density at ambient conditions, both hydrogen and natural gas are challenging to economically store onboard environmentally sustainable vehicles~\cite{?}. One strategy to densify these gases is to pack the fuel tank with a porous material~\cite{?}. Metal-organic frameworks (MOFs) are tunable, nanoporous materials with large internal surface areas and show considerable promise for densifying gases~\cite{?}. The US Department of Energy (DOE) has set volumetric deliverable capacity targets~\cite{?} which, if met, would help to enable commercial adoption of hydrogen/natural gas as transportation fuels. Many have attempted to establish theoretical upper bounds on the deliverable capacity via pressure-swing adsorption using simplified models of the gas-substrate and gas-gas interaction~\cite{?}; none have established a rigorous upper bound on the deliverable capacity.

Here, we present a theoretical upper bound on the deliverable capacity of a rigid material via an isothermal pressure-swing. 
To provide an extremum, we consider a substrate that provides a spatially uniform potential energy field for the gas. 
Our bound is unique in that it directly relies on experimentally measured properties of the (real) bulk gas, without making approximations.
We conclude that the goals set by the US DOE for natural gas and hydrogen storage are theoretically possible, but sufficiently close to the upper bound as to be impractical for any real porous material.
However, limitations to the scope of applicability of our upper bound guide future material development efforts.
Firstly, one could heat the adsorbent to drive off residual gas when the pressure diminishes~\cite{?}.
Secondly, the fundamental physics of our upper bound do not pertain to
any material that changes its structure in response to adsorbed gas, suggesting that flexible materials could still satisfy the DOE target~\cite{?}.

Consider a pressure vessel onboard a vehicle (i.e. fuel tank) packed with porous material. At the filling stage, the tank is connected and opened to a (pure) gaseous reservoir at pressure $p_\text{full}$ and allowed to equilibrate. At this point, the adsorbed gas tank is considered full. While driving, gas desorbs from the adsorbent to the engine/fuel cell, driven by a pressure differential.
The tank is considered depleted/empty when the pressure has dropped to $p_\text{empty}$, the pressure at which the flow rate of gas from the tank to the engine is insufficient.

However, given $p_\text{empty} \neq 0$ (pulling vacuum), residual gas will remain trapped in the adsorbent. Therefore, the driving range of the vehicle is primarily determined by the \emph{deliverable capacity}, defined as the density of gas in the tank at $p_\text{full}$ minus the residual gas remaining at $p_\text{empty}$. The [isothermal, volumetric] deliverable capacity is an intrinsic property of the nanoporous material and its interaction with the gas.

\jpsays{explain how 2D SAD is needed for this and how we are working toward it}

\section{Summary}
We have provided the background necessary for understanding the various flat-histogram methods and the
various applied test systems. In the following chapters, we detail our manuscripts and the method SAD
applied to the various physical test systems. We test SAD against a variety of other weight-based flat-histogram
methods on the square-well fluid, Lennard-Jones clusters, and the 2D Ising model. Each of these systems provides
unique challenges to our newly developed method SAD and convergence robustness is determined best by the application
to multiple systems.

\jpsays{Tie this in with gas adsorption!}

>>>>

% This is part of the abstract of our paper.
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard environmentally
sustainable vehicles~\cite{?}. One strategy to densify these gases is to pack
the fuel tank with a porous material~\cite{?}. Metal-organic frameworks (MOFs)
are tunable, nanoporous materials with large internal surface areas and show
considerable promise for densifying gases~\cite{?}. The US Department of Energy
(DOE) has set volumetric deliverable capacity targets~\cite{?} which, if met,
would help to enable commercial adoption of hydrogen/natural gas as
transportation fuels. Many have attempted to establish theoretical upper bounds
on the deliverable capacity via pressure-swing adsorption using simplified
models of the gas-substrate and gas-gas interaction~\cite{?}; none have
established a rigorous upper bound on the deliverable capacity.

% This is part of the abstract(s) for APS Conferences.
Here, we present a theoretical upper bound on the deliverable capacity of a
rigid material via an isothermal pressure-swing. To provide an extremum, we
consider a substrate that provides a spatially uniform potential energy field
for the gas. Our bound is unique in that it directly relies on experimentally
measured properties of the (real) bulk gas, without making approximations.
We conclude that the goals set by the US DOE for natural gas and hydrogen
storage are theoretically possible, but sufficiently close to the upper bound
as to be impractical for any real porous material. However, limitations to the
scope of applicability of our upper bound guide future material development efforts. Firstly, one could heat the adsorbent to drive off residual gas when
the pressure diminishes~\cite{?}. Secondly, the fundamental physics of our
upper bound do not pertain to any material that changes its structure in
response to adsorbed gas, suggesting that flexible materials could still
satisfy the DOE targets~\cite{?}.

% Now add why a multidimensional 2D SAD would help and how we are working toward it.

\section{Summary}
We have provided the background necessary for understanding the various
flat-histogram methods and the various applied test systems. In the following
chapters, we detail our manuscripts and the method SAD applied to the various
physical test systems. We test SAD against a variety of other weight-based
flat-histogram methods on the square-well fluid, a Lennard-Jones cluster, and
the 2D Ising model. Each of these systems provides unique challenges to our
newly developed method SAD and convergence robustness is determined best by the
application to multiple systems.
% Now tie this in with gas adsorption.
